---
title: "R Markdown Plotly"
author: "Robinson Montes Gómez"
date: "11/24/2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What is R Markdown?

R Markdown is an incredible tool for make documents or presentations combining text, plots, code and many interesting things. The output of the Markdown file could be a HTML, PDF or a PowerPoint file to make beautiful presentations for your university or a job

## Create a plot

Lets create a plot with a library called plotly, an excellent tool to make interactive plots, just writing a short line of code. For the fist plot, We'll work with the EuStockMarkets data set from the datasets library and we'll make a scatter plot

```{r, echo=TRUE, eval=FALSE}
library(datasets)
data <- as.data.frame(EuStockMarkets)
install.packages('plotly')
library(plotly)
plot_ly(data, x = ~DAX, y = ~FTSE, type = 'scatter')
```

## Scatter Plot EuStockMarkets

```{r, message=FALSE, echo=FALSE, warning=FALSE}
data <- as.data.frame(EuStockMarkets)
library(plotly)
plot_ly(data, x = ~DAX, y = ~FTSE, type = 'scatter')
```


## Last Example

```{r, message=FALSE, warning=FALSE}
data2 <- mtcars
library(plotly)
plot_ly(data2, color =  ~cyl, y = ~mpg, type = 'histogram')
```
