```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(ggplot2)
library(scales)
library(Hmisc)
```

## Loading and preprocessing the data
##### 1. Load the data
```{r, results='markup', warning=TRUE, message=TRUE}
if(!file.exists('activity.csv')){
  unzip('activity.zip')
}
data <- read.csv('activity.csv')
```
##### 2. Process/transform the data (if necessary) into a format suitable for your analysis
-----
  
## What is mean total number of steps taken per day?
```{r}
dayly_steps <- tapply(data$steps, data$date, sum, na.rm=TRUE)
```

##### 1. Make a histogram of the total number of steps taken each day
```{r}
qplot(dayly_steps, xlab='Total steps per day', ylab='Frequency using binwith 500', binwidth=500)
```

##### 2. Calculate and report the mean and median total number of steps taken per day
```{r}
mean_steps <- mean(dayly_steps)
median_steps <- median(dayly_steps)
```
* Mean: `r mean_steps`
* Median:  `r median_steps`

-----
  
## What is the average daily activity pattern?
```{r}
average_steps <- aggregate(x=list(mean_steps=data$steps), by=list(interval=data$interval), FUN=mean, na.rm=TRUE)
```

##### 1. Make a time series plot
```{r}
ggplot(data=average_steps, aes(x=interval, y=mean_steps)) +
  geom_line() +
  xlab("5-minute interval") +
  ylab("average number of steps taken") 
```

##### 2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
most_steps <- which.max(average_steps$mean_steps)
time_steps <-  gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", average_steps[most_steps,'interval'])
```

* Most Steps at: `r most_steps`

----
  
  ## Imputing missing values
  ##### 1. Calculate and report the total number of missing values in the dataset 
  ```{r}
missing_values <- length(which(is.na(data$steps)))
```

* Number of missing values: `r missing_values`

##### 2. Devise a strategy for filling in all of the missing values in the dataset.
---
##### 3. Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r}
data$steps <- impute(data$steps, fun=mean)
```


##### 4. Make a histogram of the total number of steps taken each day 
```{r}
inputed_steps <- tapply(data$steps, data$date, sum)
qplot(inuted_steps, xlab='Total steps per day (Imputed)', ylab='Frequency using binwith 500', binwidth=500)
```

##### ... and Calculate and report the mean and median total number of steps taken per day. 
```{r}
inputed_mean <- mean(inputed_steps)
inputed_median <- median(inputed_steps)
```
* Mean (Imputed): `r inputed_mean`
* Median (Imputed):  `r inputed_median`


----
  
## Are there differences in activity patterns between weekdays and weekends?
##### 1. Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
  
```{r}
data$dateType <-  ifelse(as.POSIXlt(data$date)$wday %in% c(0,6), 'weekend', 'weekday')
```

##### 2. Make a panel plot containing a time series plot

```{r}
inputed_averaged <- aggregate(steps ~ interval + dateType, data=data, mean)
ggplot(inputed_averaged, aes(interval, steps)) + 
  geom_line() + 
  facet_grid(dateType ~ .) +
  xlab("5-minute interval") + 
  ylab("avarage number of steps")
```